SPARQL on the open, decentralised Web

### 2016-06-05 dissertation/related.tex
proofread

Naturally, the problem of caching in a proxy has much in common with
the federation problem, as the cache, as seen from the query execution
engine's perspective, could be view as yet another possible data
source, and the number of HTTP requests to the remote endpoint can be
wisely assumed to be kept small. Schwarte et
al. \cite{springerlink:10.1007/978-3-642-25073-6-38} addressed these
problems with FedX, in which they sought to group connected subgraphs
with their concept of exclusive groups.  Montoya et
al. \cite{montoya2015federated} propose a query federation system that
minimise the data needed to be transferred while preserving
completeness in the common case where the data relevant to a query is
available on different endpoints. Görlitz and Staab \cite{splendid}
exploited cardinality estimates sometimes available in VoID
\cite{voidnote} descriptions to improve join order execution plans. It
could be advantageous for the system in
Chapter~\ref{sec:tpfcacheplanning} to exploit as well, and
straightforward to implement, but since it has not seen wide uptake
and the statistics is mandated by Triple Pattern Fragments, and
therefore available in some cases to the planner, we chose not to.

@@

Dividino et al. \cite{Dividino2015} proposed strategies to keep caches
of Linked Open Data up to date, in face of changing data. The authors
sets out to learn the change frequency of resources, and based on that
schedule updates of the resources. This does then not depend on the
resource metadata (neither HTTP headers nor metadata in the RDF
itself, which I studied in \cite{kjernsmo_survey_2015}), which is
motivated by their finding that only 8\% of \httph{Last-Modified}
headers they surveyed reflected the true change frequency. While I
have no reason to doubt this finding, and the monitoring approach is
interesting, I think the dismissal of resource metadata is
insufficiently motivated, and therefore the evaluation is
inadequate. First, the \httph{Last-Modified} header is far from the
only cache-relevant header, as should be evident by the fact that it
is not defined in the cache standard, RFC7234, but in the conditional
request standard, RFC7232. Moreover, RFC7234 contains a Section~4.2.2.
titled ``Calculating Heuristic Freshness''. It is my opinion that the
paper should be framed within the loose constraints of this section,
where it could make a substantial contribution. As it stands, it would
serve to violate Web standards, which in my opinion, is something the
Semantic Web community should be more cautious about. RFC7234's
Section~4.2.2. also proposes a simple heuristic for calculating
freshness lifetime. I found that the distribution of this heuristic
freshness lifetime agrees well with The Dynamic Linked Data
Observatory (DyLDO) \cite{dyldo2}. However, a weakness of my study
which could make this observation irrelevant, is that I considered
only summary statistics. If the change frequency of individual
resources were wrong, in particular, if the use of the simple
heuristic lead to using stale content, it would be inappropriate to
use the simple heuristic.  RFC7234's explicitly prohibits the use of a
heuristic if an explicit expiration time is present, yet the paper
does not attempt to include those in their assessment. Furthermore, I
found in \cite{kjernsmo_survey_2015} that cache prohibitions were
common. While they in many cases may be misguided, they nevertheless
express a strong statement from the server administrators, that should
be respected. RDF data, e.g. \rdfterm{dct:valid} and
\rdfterm{dct:modified} could also be used to compute a expiration
time. Finally, an opaque validator, \httph{ETag} is also a part of
RFC7232. After considering cache prohibitions, explicit expiration
times, opaque validators, simpler heuristics, etc., the space where
learning the change frequency could be applied is likely much
smaller. However, if understood as a sophisticated heuristic within
the constraints of RFC7234's Section~4.2.2., the contribution is
valuable.

>>>>

Naturally, the problem of caching in a proxy has much in common with
the federation problem as the cache, as seen from the query execution
engine's perspective, could be viewed as yet another possible data
source, and the number of HTTP requests to the remote endpoint can be
wisely assumed to be kept small. Schwarte et
al. \cite{springerlink:10.1007/978-3-642-25073-6-38} addressed these
problems with FedX, in which they sought to group connected subgraphs
with their concept of exclusive groups.  Montoya et
al. \cite{montoya2015federated} propose a query federation system that
minimise the data needed to be transferred while preserving
completeness in the common case where the data relevant to a query is
available on different endpoints. Görlitz and Staab \cite{splendid}
exploited cardinality estimates sometimes available in VoID
\cite{voidnote} descriptions to improve join order execution plans. It
could be advantageous for the system in
Chapter~\ref{sec:tpfcacheplanning} to exploit as well, and
straightforward to implement, but since it has not seen wide uptake
and the statistics is mandated by Triple Pattern Fragments, and
therefore available in some cases to the planner, we chose not to.

@@

Dividino et al. \cite{Dividino2015} proposed strategies to keep caches
of Linked Open Data up to date, in face of changing data. The authors
sets out to learn the change frequency of resources, and based on that
schedule updates of the resources. This does then not depend on the
resource metadata (neither HTTP headers nor metadata in the RDF
itself, which I studied in \cite{kjernsmo_survey_2015}), which is
motivated by their finding that only 8\% of \httph{Last-Modified}
headers they surveyed reflected the true change frequency. While I
have no reason to doubt this finding, and the monitoring approach is
interesting, I think the dismissal of resource metadata is
insufficiently motivated, and therefore the evaluation is
inadequate. First, the \httph{Last-Modified} header is far from the
only cache-relevant header, as should be evident by the fact that it
is not defined in the cache standard, RFC7234, but in the conditional
request standard, RFC7232. Moreover, RFC7234 contains a Section~4.2.2
titled ``Calculating Heuristic Freshness''. It is my opinion that the
paper should be framed within the loose constraints of this section,
where it could make a substantial contribution. As it stands, it would
serve to violate Web standards, which in my opinion, is something the
Semantic Web community should be more cautious about. RFC7234's
Section~4.2.2 also proposes a simple heuristic for calculating
freshness lifetime. I found that the distribution of this heuristic
freshness lifetime agrees well with The Dynamic Linked Data
Observatory (DyLDO) \cite{dyldo2}. However, a weakness of my study
which could make this observation irrelevant, is that I considered
only summary statistics. If the change frequency of individual
resources were wrong, in particular, if the use of the simple
heuristic lead to using stale content, it would be inappropriate to
use the simple heuristic.  RFC7234's explicitly prohibits the use of a
heuristic if an explicit expiration time is present, yet the paper
does not attempt to include those in their assessment. Furthermore, I
found in \cite{kjernsmo_survey_2015} that cache prohibitions were
common. While they in many cases may be misguided, they nevertheless
express a strong statement from the server administrators, that should
be respected. RDF data, e.g. \rdfterm{dct:valid} and
\rdfterm{dct:modified} could also be used to compute a expiration
time. Finally, an opaque validator, \httph{ETag} is also a part of
RFC7232. After considering cache prohibitions, explicit expiration
times, opaque validators, simpler heuristics, etc., the space where
learning the change frequency could be applied is likely much
smaller. However, if understood as a sophisticated heuristic within
the constraints of RFC7234's Section~4.2.2, the contribution is
valuable.
